Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
mino edit to Ken comment

\ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted. Such a choice is usually based on the principle of parsimony \cite{Illfindit}, that is; the simplest model capable of capturing the system behaviour of interest is chosen. Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.}

>>>>

\ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted. Such a choice is usually based on the principle of parsimony \cite{Illfindit}, that is; choosing the simplest model capable of capturing the system behavior of interest. Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.}
